%Abstract like thing?
The binding corrections to the gyromagnetic ratio $g$ are investigated for a particle of arbitrary spin.  The corrections are worked out for specific spin-half and spin-one theories, before considering the more general case.  By considering the constraints lying upon the relativistic theory, an effective nonrelativistic Lagrangian is developed.

\chapter{Introduction}
A way to calculate the binding corrections to the $g$-factor of a charged particle of arbitrary spin is desired.

The $g$ factor in this sense is defined by the energy separation of two particles which differ only by spin orientation.  A free electron, with its spin oriented along the same axis as a magnetic field $B_z\hat{z}$, has energy
\beq
 E = - \gv{\mu} \cdot \v{B} = - g \frac{e}{2m}s_z B_z
\eeq
The difference between such an electron and one with its spin flipped is then
\beq
	\delta E = - g \frac{e}{m}s_z B_z = -g \mu_B B
\eeq

The general definition of the $g$-factor then follows -- the energy difference between two particles with spin projection parallel and anti-parallel to a small constant magnetic field will be proportional to $ - \mu_B B$, and the coefficient of this difference defines the $g$-factor.

Of interest here is the $g$ factor of a bound state system, which will differ from that of a free particle.  There will be several types of corrections to the free $g$-factor.

We wish to calculate the gyromagnetic ratio of a particle of arbitrary spin in a loosely bound state system.  We can write down an effective Lagrangian which will capture all the necessary effects.  Our job is then to calculate the coefficients of this effective particle.  By considering the constraints which exist on the electromagnetic current in a general relativistic theory, we can obtain a simple form which holds for arbitrary spin, and then use this to fix the coefficients of the relativistic theory.

While for a particle of general spin we do not have an exact Lagrangian, we do have one for a spin-$1$ theory.  We can use this Lagrangian to perform the same calculation as above, but in an exact theory.  We derive the nonrelativistic potential first from the equations of motion, and then from diagrammatic calculations, and obtain a result that agrees with the more general calculation.  
\subsection{Description of problem}
We consider a loosely bound system two particles of arbitrary spin, and wish to calculate the correction to the gyromagnetic ratio of the particles.  So we consider the case of the two particles interacting with both each other, via a Coulomb potential, and a very weak external magnetic field.
\subsubsection{Experimental Motivation}

Talk about 


\subsubsection{Approach}
This system allows for several simplifications.  First, because the system is loosely bound all energy scales are nonrelativistic.  
%TODO details of nonrelativistic nature
Second, the magnetic field we consider is both very weak and constant.  So we can ignore all corrections which involve derivatives of the magnetic field or which are quadratic in its strength.

The approach we'll take is to first consider the electric potential as an external field acting on a single particle.  Next we can consider the bound system as a whole sitting in an external magnetic field, and take into account recoil effects.

%Discuss to what order we need to do the calculations

\subsection{Theoretical Background}

(Here we talk about existing theoretical work in this area)
\subsubsection{Spin-$1/2$}

(Here talk about the approach that works for spin 1/2, and why it breaks down in the general case.)

\subsubsection{BMT equation}

(Here discuss the BMT equation, which holds for general spin and can be used to derive the g-factor corrections)

\subsubsection{Khriplovich general spin work}
(Discuss the work Khriplovich did with general spinors.)
