\documentclass[margin,line]{res}


\oddsidemargin -.5in
\evensidemargin -.5in
\textwidth=6.0in
\itemsep=0in
\parsep=0in

\newenvironment{list1}{
  \begin{list}{\ding{113}}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in} 
      \setlength{\leftmargin}{0.17in}}}{\end{list}}
\newenvironment{list2}{
  \begin{list}{$\bullet$}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in} 
      \setlength{\leftmargin}{0.2in}}}{\end{list}}


\begin{document}

\name{Timothy J. S. Martin \vspace*{.1in}}

\begin{resume}
\section{\sc Contact Information}
\vspace{.05in}
\begin{tabular}{@{}p{2in}p{4in}}
Chemistry-Physics 390            & {\it Voice:}  (859) 684-8715 \\            
Department of Physics   & {\it E-mail:}  tjmart1@uky.edu\\         
University of Kentucky & \\    
Lexington, KY 40506  &     \\
\end{tabular}


\section{\sc Research Interests}
Theoretical particle physics.  Bound state theory in QED.

\section{\sc Education}
{\bf University of Kentucky}, Lexington, Kentucky USA\\
%{\em Department of Statistics} 
\vspace*{-.1in}
\begin{list1}
\item[] Ph.D., Physics, Fall 2011
\begin{list2}
\vspace*{.05in}
\item Dissertation Topic:  ``Universal Binding and Recoil Corrections to Bound State $g$-Factors''
%\item Dissertation Topic:  ``Hierarchical Models for Multiple Ratings
%  in Performance-Based\\ \hspace*{1.23in} Student Assessments.'' 
\item Advisor:  Michael Eides
\end{list2}
\vspace*{.05in}
\item[] M.S., Physics,  May 2009
\end{list1}

\begin{list1}
\item[] B.S., Physics and Math,  May, 2005
\end{list1}






%\section{\sc Honors and Awards} 
%National Science Foundation Graduate Research Fellowship, 1996

%\vspace*{-2.5mm}
%NSF Vertical Integration of Research and Education in Statistics and
%Mathematical Sciences\\ (VIGRE) teaching fellowship.
%
%\vspace*{-2.5mm}
%Carleton College: graduated Magna Cum Laude, Honors in Biology, Phi Beta Kappa, 1993

\section{\sc Academic Experience}
{\bf University of Kentucky}, Lexington, Kentucky USA

\vspace{-.3cm}
{\em Graduate Student} \hfill {\bf August, 2005 - 2011}\\
Ph.D.~research, Ph.D.~and Masters level coursework.

%\vspace{-.1cm}
{\em Teaching Assistant} \hfill {\bf August, 2005  - 2009}\\
Duties have included teaching recitation and labs, grading tests, and setting quizzes.  Classes taught have included both {\it{College Physics}} and {\it{Physics for Scientists and Engineers}}.



\section{\sc Publications and Presentations}
Michael I. Eides and Timothy J.S. Martin.  2010.  Universal Binding and Recoil Corrections to Bound State g Factors in Hydrogenlike Ions.  Physical Review Letters.  105:100402

Michael I. Eides and Timothy J.S. Martin.  2011.  Universality of Leading Relativistic Corrections to Bound State Gyromagnetic Ratios.  Canadian Journal of Physics.  89(1): 117




\section{\sc Computer Skills} 
\begin{list2}
\item Languages:  C, C++, Java, Javascript
\item Applications: Mathematica, Maple, and Octave; \LaTeX; common office software
\item Operating Systems:  Linux, OS X, Windows\\ 
\end{list2}



\end{resume}
\end{document}




